### 2016-09-02 R/ITHIM.Rmd
Fixed bug in HHS mapping

NHTS.person <- with(PERV2PUB,{
                    data.frame(HOUSEID = HOUSEID,
                               PERSONID = PERSONID,
                               SEX = as.factor(ifelse(R_SEX=="1", "M", ifelse(R_SEX=="2", "F", NA))),
                               AGE = as.factor(convertToAgeClass(R_AGE)),
                               MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                               HHS = as.factor(convertToHHS(HHSTATE))

@@

burden <- merge(HHSmetroCauseSpecific, USGBD, all.x=T)
burden$deaths <- burden$numberOfDeaths5yr/5
burden$ratio <- ifelse(burden$GBDdeaths == 0, 1, ((burden$deaths/burden$population2014)/(burden$GBDdeaths/burden$GBDpop)))
burden$YLL <- burden$ratio * (burden$GBDyll/burden$GBDpop) * burden$population2014
burden$YLD <- burden$ratio * (burden$GBDyld/burden$GBDpop) * burden$population2014
burden$DALY <- burden$ratio * (burden$GBDdaly/burden$GBDpop) * burden$population2014

@@

p1 <- ggplot(D, aes(x = ageClass, y = time, fill = sex)) + geom_bar(stat= "identity", position = "dodge") + facet_grid( mode ~ HHS)

>>>>

NHTS.person <- with(PERV2PUB,{
                    data.frame(HOUSEID = HOUSEID,
                               PERSONID = PERSONID,
                               SEX = as.factor(ifelse(R_SEX=="1", "M", ifelse(R_SEX=="2", "F", NA))),
                               AGE = as.factor(convertToAgeClass(R_AGE)),
                               MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                               HHSTATE = as.character(HHSTATE),
                               HHS = as.character(convertToHHS(as.character(HHSTATE))), stringsAsFactors = FALSE

@@

burden <- merge(HHSmetroCauseSpecific, USGBD, all.x=T)
burden$deaths <- burden$numberOfDeaths5yr/5
## neil uses 10, and if deaths<10 sets ratio to 1
burden$ratio <- ifelse(burden$GBDdeaths == 0, 1, ((burden$deaths/burden$population2014)/(burden$GBDdeaths/burden$GBDpop)))
burden$YLL <- burden$ratio * (burden$GBDyll/burden$GBDpop) * burden$population2014
burden$YLD <- burden$ratio * (burden$GBDyld/burden$GBDpop) * burden$population2014
burden$DALY <- burden$ratio * (burden$GBDdaly/burden$GBDpop) * burden$population2014

@@

p1 <- ggplot(D, aes(x = ageClass, y = time, fill = sex)) + geom_bar(stat= "identity", position = "dodge") + facet_grid( mode ~ HHS, scales = "free_y")
